### 2020-06-25 README.Rmd
About to relaunch full simulation

```{r, eval = FALSE}
# Number of permutation shuffles:
num_shuffle <- 2

@@

# Save results here
run_time <- rep(0, length(species_notion_vector))
observed_RMSE <- rep(0, length(species_notion_vector))
observed_RMSE_CV <- rep(0, length(species_notion_vector))
shuffle_RMSE <- list()
shuffle_RMSE_CV <- list()

@@

  # Modeling and species stuff
  model_number <- 3
  species_notion <- species_notion_vector[i]
  bw_specs <- bw_growth_df %>% 
    get_model_specs(model_number = model_number, species_notion = species_notion)

@@

  # 3. Permutation distribution: RMSE with no cross-validation ----
  # Only do permutation shuffling for models 3, 6, 9
  if(model_number %in% c(3, 6, 9)){
    # Compute num_shuffle permutation test statistics
    shuffle_RMSE[[i]] <- numeric(length = num_shuffle)

@@

      # Make predictions, compute and save RMSE, and reset
      shuffle_RMSE[[i]][j] <- focal_vs_comp_bw %>% 
        predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model_shuffle) %>% 
        right_join(bw_growth_df_orig, by = c("focal_ID" = "treeID")) %>%
        rmse(truth = growth, estimate = growth_hat) %>%
        pull(.estimate)
    }
  } else {
    shuffle_RMSE[[i]] <- NA
  }

  # 4. Permutation distribution: RMSE with cross-validation ----
  # Only do permutation shuffling for models 3, 6, 9
  if(model_number %in% c(3, 6, 9)){
    # Compute num_shuffle permutation test statistics
    shuffle_RMSE_CV[[i]] <- numeric(length = num_shuffle)

@@

      # Status update
      str_c("notion of species: ", species_notion_vector[i], ", shuffle with permutation ", j) %>% print()
    }
  } else {
    shuffle_RMSE_CV[[i]] <- NA
  }

  # 5. Stop clock and save
  clock <- toc(quiet = TRUE)
  run_time[i] <- clock$toc - clock$tic
}

model_comp_tbl <- tibble(
  model_number = model_numbers,
  run_time = run_time,
  observed_RMSE = observed_RMSE,
  observed_RMSE_CV = observed_RMSE_CV,
  shuffle_RMSE = shuffle_RMSE,
  shuffle_RMSE_CV = shuffle_RMSE_CV,
)

save(model_comp_tbl, file = str_c(format(Sys.time(), "%Y-%m-%d"), "_model_comp_tbl_", num_shuffle, "_shuffles.RData"))
```

@@

```{r}
load("model_comp_tbl_4_shuffles.RData")
model_comp <- bind_rows(
  model_comp_tbl %>% select(model_number, run_time, observed = observed_RMSE, shuffle = shuffle_RMSE) %>% mutate(CV = FALSE),
  model_comp_tbl %>% select(model_number, run_time, observed = observed_RMSE_CV, shuffle = shuffle_RMSE_CV) %>% mutate(CV = TRUE)
) %>%
  gather(type, RMSE, -c(model_number, run_time, CV)) %>%
  arrange(CV, model_number) %>%
  mutate(
    model_number = case_when(
      model_number == 3 ~ "1. Trait-based (6): lambda = 6 x 6",
      model_number == 6 ~ "2. Phylogenetic family (20): lambda = 20 x 20",
      model_number == 9 ~ "3. Actual species (36): lambda = 36 x 36"
    )
  )

model_comp_observed <- model_comp %>%
  filter(type == "observed") %>%
  unnest()
model_comp_shuffle <- model_comp %>%
  filter(type == "shuffle") %>%
  unnest()

@@

ggplot() +
  geom_vline(data = model_comp_observed, aes(xintercept = RMSE, col = CV), linetype = "dashed", show.legend = F) +
  geom_histogram(data = model_comp_shuffle, aes(x = RMSE, fill = CV), bins = 200) +
  labs(fill = "Cross-validated?", x = xlab) +
  facet_wrap(~model_number, ncol = 1) +
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE)
```

>>>>

```{r, eval = FALSE}
# Number of permutation shuffles:
num_shuffle <- 4

@@

# Save results here
run_time <- rep(0, length(species_notion_vector))
observed_RMSE <- rep(0, length(species_notion_vector))
observed_RMSE_CV <- rep(0, length(species_notion_vector))
shuffle_RMSE <- vector("list", length(species_notion_vector))
shuffle_RMSE_CV <- vector("list", length(species_notion_vector))
filename <- str_c(format(Sys.time(), "%Y-%m-%d"), "_model_comp_tbl_", num_shuffle, "_shuffles.RData")

@@

  # Modeling and species stuff
  species_notion <- species_notion_vector[i]
  bw_specs <- bw_growth_df %>% 
    get_model_specs(model_number = 3, species_notion = species_notion)

@@

  # 3. Permutation distribution: RMSE with no cross-validation ----
  # Only do permutation shuffling for models 3, 6, 9
  # Compute num_shuffle permutation test statistics
  shuffle_RMSE[[i]] <- numeric(length = num_shuffle)

@@

    # Make predictions, compute and save RMSE, and reset
    shuffle_RMSE[[i]][j] <- focal_vs_comp_bw %>% 
      predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model_shuffle) %>% 
      right_join(bw_growth_df_orig, by = c("focal_ID" = "treeID")) %>%
      rmse(truth = growth, estimate = growth_hat) %>%
      pull(.estimate)
  }

  # 4. Permutation distribution: RMSE with cross-validation ----
  # Compute num_shuffle permutation test statistics
  shuffle_RMSE_CV[[i]] <- numeric(length = num_shuffle)

@@

    # Status update
    str_c("notion of species: ", species_notion_vector[i], ", shuffle with permutation ", j) %>% print()
  }

  # 5. Stop clock
  clock <- toc(quiet = TRUE)
  run_time[i] <- clock$toc - clock$tic

  # 6. Save
  model_comp_tbl <- tibble(
    species_notion = species_notion_vector,
    run_time = run_time,
    observed_RMSE = observed_RMSE,
    observed_RMSE_CV = observed_RMSE_CV,
    shuffle_RMSE = shuffle_RMSE,
    shuffle_RMSE_CV = shuffle_RMSE_CV,
  )
  save(model_comp_tbl, file = filename)
}
```

@@

```{r, eval=FALSE}
load("model_comp_tbl_4_shuffles.RData")
model_comp <- bind_rows(
  model_comp_tbl %>% select(species_notion, run_time, observed = observed_RMSE, shuffle = shuffle_RMSE) %>% mutate(CV = FALSE),
  model_comp_tbl %>% select(species_notion, run_time, observed = observed_RMSE_CV, shuffle = shuffle_RMSE_CV) %>% mutate(CV = TRUE)
) %>%
  gather(type, RMSE, -c(species_notion, run_time, CV)) %>%
  arrange(CV, model_number) %>%
  mutate(
    species_notion = case_when(
      species_notion == "trait_group" ~ "1. Trait-based (6): lambda = 6 x 6",
      species_notion == "family" ~ "2. Phylogenetic family (20): lambda = 20 x 20",
      species_notion == "species" ~ "3. Actual species (36): lambda = 36 x 36"
    )
  )

model_comp_observed <- model_comp %>%
  filter(type == "observed") %>%
  unnest(cols = c(RMSE))
model_comp_shuffle <- model_comp %>%
  filter(type == "shuffle") %>%
  unnest(cols = c(RMSE))

@@

ggplot() +
  geom_vline(data = model_comp_observed, aes(xintercept = RMSE, col = CV), linetype = "dashed", show.legend = F) +
  geom_histogram(data = model_comp_shuffle, aes(x = RMSE, fill = CV), bins = 200) +
  labs(fill = "Cross-validated?", x = xlab) +
  facet_wrap(~species_notion, ncol = 1) +
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE)
```
